Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-12-11 parts/sa.tex
begin extraction of the scenario

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as: $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subseteq \cwV \label{eq:Vw} \\
    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \cwVObj \wedge ps \in \BS(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
  \end{align}
\end{definition}

@@

>>>>

\begin{definition}
\label{def:glc}
  The graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as: $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subseteq \cwV \label{eq:Vw} \\
    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \cwVObj \wedge ps \in \modMF{\aBS}(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
  \end{align}
\end{definition}

@@

\modMF{
\subsection{Extraction of the scenario}
}

\modMF{
This section gives a recursive method to find a scenario that concretizes
a given objective sequence $\w \in \OS$.
All the definitions above are well-defined provided that
$\uconcr(\w)\neq\emptyset$,
which can be demonstrated by \pref{thm:ordered-ua} or \pref{th:approxinf}.
The justification of these definitions can be found by analysing the demonstrations
of these theorems.
}

\newcommand{\res}{\mathbf{res}}
\newcommand{\osres}{\mathbf{OSres}}
\newcommand{\autoBS}{\mathbf{autoBS}}
\newcommand{\rec}{\mathbf{rec}}
\newcommand{\thisobj}[1]{P_{#1}}
\newcommand{\thisseq}[1]{\Theta_{#1}}

\modMF{
For all $\w \in \OS$:
\[
  \osres_s(\w) = \res_s(\w_1) \concat
    \osres_{s \play \res_s(\w_1)}(\w_2 \concat \dots \concat \w_{\card{\w}})
\]
with $\osres_s(\varepsilon) = \varepsilon$.
For all $P \in \Obj$:
\[\res_s(P) =
  \begin{cases}
    \varepsilon
      & \text{if } \target{P} = \bounce{P} \\
%     pickone(\autoBS(P))
%       & \text{if } \aBS(P) = \{ \emptyset \} \\
    \osres_s(P^Q \concat Q)
      & \text{if } \exists Q \in \Obj, (P, Q) \in \Bee{\Obj}{\Obj} \\
    \rec_s(\zeta)
      & \text{otherwise, with } \zeta \in \BS(P)
  \end{cases}
\]
where:
\[
  \autoBS(P) = \{ \zeta \in \BS(P) \mid \forall i \in \indexes{\zeta}, \PHsort(\hitter{\zeta_i}) = \PHsort(\target{\zeta_i}) = \PHsort(P) \}
\]
\[
  P^Q = \PHobj{\PHtarget(P)}{\PHtarget(Q)}
\]
\[
  \rec_s(\zeta) = \thisseq{\zeta_1} \play
    \rec_{s \play \thisseq{\zeta_1}}
    (\zeta_2 \concat \dots \concat \zeta_{\card{\zeta}})
\]
with:
\[
  \thisseq{h} = \res_s(\thisobj{h}) \play
    \delta^{upd}_{s \play \res_s(\thisobj{h})} \play h
\]
\[
  \thisobj{h} = \PHobj{\PHget{s}{\PHsort(\hitter{h})}}{\hitter{h}}
\]
and $\delta^{upd}_{s'}$ is a scenario of actions in $\PHh^{(1)}$ that updates
all cooperative sorts from state $s'$.
Such a scenario always exists given \pref{lem:update},
and it can be built, starting from $s'$
by iteratively putting arbitrary prioritized actions into a sequence
until no more prioritized action is playable.
Indeed, the order of the actions do not matter and the final state will
always be $\update(s')$.
}

\todo{À terminer et gluer}
